Validating risk scores - Czech data

### 2021-04-06 other_outputs/risk_scores_consortium.Rmd
Updating Wang model, summary

```{r}
wang_clinical <- function(data) {
  data %>%
    mutate(hypertension = n_hypertension_drugs > 0,
           lp =
  -2.6551 + 0.10 * age + 0.60 * hypertension + 1.11 * (ischemic_heart_disease == "TRUE")) %>%
    pull(lp)
}
```

@@

```{r}
```

Xie - not sure if using SpO2 or SpO2 native
DDU vs FEU D-dimer

>>>>

```{r}
wang_clinical <- function(data) {
  data %>%
    mutate(hypertension = n_hypertension_drugs > 0,
           lp =
  -8.6 + 0.10 * age + 0.60 * hypertension + 1.11 * (ischemic_heart_disease == "TRUE")) %>%
    pull(lp)
}
```

@@

# Summaries

```{r}
data_risk_sum <- data_risk %>% mutate(sex_male = sex == "M",
                                      hypertension = n_hypertension_drugs > 0,
                                      deceased = mortality == "dead")

binary_columns <- c(
 "sex_male",
 "hypertension",
 "heart_failure",
 "COPD",
 "asthma",
 "other_lung_disease",
 "diabetes",
 "renal_disease",
 "liver_disease",
 "smoking",                  
 "admitted_for_covid",
 "ischemic_heart_disease",
 "deceased"
)

continuous_columns <- c(
 "age" ,
 "days_from_symptom_onset",
 "BMI",                
 "AST",
 "CRP",
 "lymphocyte_count",
 "neutrophile_count",
 "platelet_count",
 "d_dimer",
 "ferritin",
 "IL_6",
 "lactate_dehydrogenase",
 "procalcitonin",
 "leukocyte_count",
 "creatinin",
 "pt_inr", 
 "albumin"
)

summary_binary_list <- list()

for(col in binary_columns) {
  vals <- data_risk_sum[[col]]
  if(is.factor(vals)) {
    if(identical(levels(vals), c("FALSE", "TRUE"))) {
      vals <- vals == "TRUE"
    } else {
      stop("Factor with invalid levels")
    }
  }
  if(!is.logical(vals)) {
    stop(col, " is not logical")
  }
  summary_binary_list[[col]] <- data.frame(
    name = col,
    type = "binary",
    n_missing = sum(is.na(vals)),
    mean = mean(vals, na.rm = TRUE)
  )
}

summary_binary <- do.call(rbind, summary_binary_list)

summary_continuous_list <- list()
for(col in continuous_columns) {
  vals <- data_risk_sum[[col]]
  if(!is.numeric(vals)) {
    stop(col, " is not numeric")
  }
  summary_continuous_list[[col]] <- data.frame(
    name = col,
    type = "continuous",
    n_missing = sum(is.na(vals)),
    mean = mean(vals, na.rm = TRUE)
  )
}

summary_continuous <- do.call(rbind, summary_continuous_list)

summary_all <- rbind(summary_binary, summary_continuous)
summary_all

write_csv(summary_all, path = here::here("local_temp_data", "table_1_summary.csv"))
```
